---
title: "Epidemiological situation of COVID-19 in the Netherlands"
output: html_document
---

```{r setup_chunks, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)
```

```{r setup_library, include=FALSE}
library(kableExtra)
library(patchwork)
```

`r format(date_report, "%e %B %Y")`  
\
**Disclaimer**:\
This report is merely illustrative. Official reports on the COVID-19 epidemiological situation in the Netherlands can be found [here](https://www.rivm.nl/coronavirus-covid-19/actueel/wekelijkse-update-epidemiologische-situatie-covid-19-in-nederland).

\
\
\
\
\
\

##### **COVID-19 notifications**\
Source: [RIVMdata](https://data.rivm.nl/meta/srv/eng/catalog.search;jsessionid=7E3B438E1812BD5F2AE74734A9B43230#/metadata/2c4357c8-76e4-4662-9574-1deb8a73f724).

\
\

Number of COVID-19 notifications per day in the last complete week  
```{r table_notifications_number_per_day_last_7days_average_total, echo=FALSE}
table_notifications_number_per_day_last_7days_average_total %>%
  rename(
    `Date of statistics` = date_statistics,
    `Number of notifications` = number_notifications
  ) %>%
  kable(
    booktabs = T, linesep = "",
    caption = ""
  ) %>%
  kable_styling(latex_options = c("hold_position"), font_size = 14) %>%
  column_spec(1:2, width = "50mm")
```

\
Number of COVID-10 notifications per week since `r format(date_start_last_wave, "%e %B %Y")`  
```{r graph_notifications_number_per_week, echo=FALSE}
graph_notifications_number_per_week %>% 
  ggplotly()
```

\
Number of COVID-10 notifications per age group, per week since `r format(date_start_last_wave, "%e %B %Y")`
```{r graph_notifications_incidence_per_week_per_age_group, echo=FALSE}
graph_notifications_incidence_per_week_per_age_group %>% 
  ggplotly()
```

\
Number of COVID-10 notifications per province inhabitants in the last complete week  
```{r map_notifications_incidence_per_province_last_week, echo=FALSE}
map_notifications_incidence_per_province_last_week
```

\
\
\
\
\
\

##### **SARS-CoV-2 tests**\
Source: [RIVMdata](https://data.rivm.nl/meta/srv/eng/catalog.search;jsessionid=7E3B438E1812BD5F2AE74734A9B43230#/metadata/0f3336f5-0f16-462c-9031-bb60adde4af1).

\
\
Number of SARS-CoV-2 tests with results and positive tests (A) and percentage positive tests (B) per week since `r format(date_expansion_testing, "%e %B %Y")`  
```{r graph_tests_number_results_positive_per_week, echo=FALSE}
graph_tests_number_results_positive_per_week / graph_tests_percentage_positive_per_week +
  plot_annotation(tag_levels = "A")
```

\
Percentage positive tests per province in the last complete week  
```{r graph_tests_percentage_positive_per_province_last_week, echo=FALSE}
map_tests_percentage_positive_per_province_last_week
```

